Multispecies survey for diet comp

### 2020-12-18 SurveyDietCompTest.Rmd
test new wrapper and compare surveys

om_diet<- function(config = configfile,
                   dietfile = file_diet,
                   fgs = fgs,
                   usersurvey = usersurvey_file,
                   userfishery = NULL,
                   omlist_ss,
                   n_reps = n_reps,
                   unidprey = 0,
                   alphamult = 10000000,
                   save = TRUE){

@@

@@

>>>>

om_diet<- function(config = configfile,
                   dietfile = file_diet,
                   usersurvey = usersurvey_file,
                   omlist_ss,
                   n_reps = n_reps,
                   save = TRUE){

  source(config)

  #Load functional groups
  fgs <- atlantisom::load_fgs(dir=d.name,
                                       file_fgs = functional.groups.file)

@@

  return(survObsDiets)

@@

## Test wrapper

The new `om_diet` function should load the detailed diet file, run the survey, then sample the diets and save outputs for each survey. This takes 3 minutes to run with two surveys and 10 species.

```{r testwrapper, eval=FALSE}

NOBAom_ms <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))

NOBAom_ms_diet <- om_diet(config = here("config", "NOBA2config.R"),
                          dietfile = "NOBADetDiet.gz",
                          usersurvey = c(here("config/mssurvey_spring_01.R"), 
                                         here("config/mssurvey_fall_01.R")), 
                          omlist_ss = NOBAom_ms, 
                          n_reps = 1, 
                          save = TRUE)

### Compare spring and fall surveys {.tabset}

The diet was sampled with alphamult = 10 and unidprey = 0.3 using the survey configuration files.

NOBAom_ms_diet <- read_savedsurvs(d.name, 'survDiet')

preds <- unique(unique(NOBAom_ms_diet[[2]][[1]]$species))

fall <- as.data.frame(NOBAom_ms_diet$BTS_fall_nearbox_qmix_selmix[[1]])
spring <- as.data.frame(NOBAom_ms_diet$BTS_spring_nearbox_qmix_selmix[[1]])

for(i in 1:length(preds)) {
  cat("  \n####",  as.character(preds[i]),"  \n")
  print(plotdiet(dat = filter(spring, species %in% preds[i]), namedat = "Spring survey diet", compdat = filter(fall, species %in% preds[i]), namecomp = "Fall survey diet")) 
  cat("  \n")
}
